\bf Supplementary Material to\\ ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''

### 2025-10-04 manuscript/manuscript.tex
described investigation in reply letter
revixed section 2.4 and replied AE

\subsection{Heuristic justification for the bias correction term in NPBB}

@@

% This approach extends the logic of \citet{babu2004goodness}, who
% introduced a similar correction for independent data, to the context
% of serially dependent time series via block bootstrapping.
% The bias correction term $C_n(x)$ used in the NPB method for
% independent data could, in principle, also be approximated by a
% bootstrap expectation in the same way as $K_n(x)$.
% Nonetheless, under independence, the empirical distribution $F_n(x)$
% and the parameter estimate $\hat{\theta}_n$ are already reliable, so
% direct calculation of $C_n(x)$ is both simpler and sufficient. The use
% of bootstrap expectations as in $K_n(x)$ becomes necessary only when
% serial dependence distorts the properties of $F_n(x)$, making
% block-bootstrapping-based bias estimation essential.

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with seven levels of Kendall's
$\tau \in \{-.75, -.5, -.25, 0, .25, .5, 75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence between $X_i$ and
$X_{i+1}$ as it is invariant to monotone marginal
transformations.
To generate the samples to which our
method would be applied, we simulated a time series $W_i$ from a 1st
order autoregressive or AR(1) process:
\begin{equation*}
W_i = \phi W_{i-1} + \epsilon_i,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_i$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels:
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. The
series $W_i$ has mean zero and variance
$\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
$\phi$,  we
set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_i$ by
\begin{equation*}
X_i = F^{-1}[\Phi(W_i)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$
distribution and $\Phi$ is the distribution function of the standard normal
distribution.
Then we generated a marginal gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution. After the transformation
to the marginal gamma distribution, the lag-1 autocorrelations are approximately
\[
  \{-0.876, -0.674, -0.368, 0, 0.377, 0.701, 0.922\}.
\]

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions
are very similar and their first two moments are the same. For the purposes of
evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
marginal distribution is from the
Normal family, or
$X_i \sim N(\cdot ; \mu, \sigma^2), \quad i = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_i \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_i \sim \Gamma(\cdot ; \alpha, \beta), \quad i = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
As noted in Subsection~\ref{sub:npbb}, previous literature
suggests varying block size based on the dependence structure of the series.
For this reason,
we also tried implementing our algorithm using the plug-in approach for circular
bootstrap block size introduced in \citet{politis2004automatic}. Results and
a discussion of this additional simulation are provided in a supplement.
We also compared empirical performance for the block bootstrap KS test when using the $K_n(x)$ correction
versus the $C_n(x)$. The $K_n(x)$ correction was used
in the main manuscript whereas results and a discussion for the
$C_n(x)$ correction is included in the supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method 10000 times
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating process.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already
found that our method doesn't work under the null hypothesis for such high
dependence levels under the sample sizes considered. It appears that the
rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial
dependence, but they do not seem to be affected by negative serial dependencies
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in
rejection rates close to 1 for $0.5 < \tau < 0.5$.
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very
high (almost 1), indicating that under $H_A$, the test is very powerful
when a large enough sample size is used.

@@

>>>>

\subsection{Heuristic justification for the NPBB bias correction}

@@

Theoretically, $K_n(x)$ and the simpler plug--in correction
$C_n(x)=\sqrt{n}\{F_n(x)-F(x;\hat\theta_n)\}$ are asymptotically
equivalent when the series is independent or exhibits only
short--memory dependence.  The joint process of $(F_n,\hat\theta_n)$
converges to a mean--zero Gaussian limit whose long--run covariance
aggregates auto--covariances across lags.  When the circular block
bootstrap reproduces this long--run covariance, the conditional bias of
the plug--in statistic is of smaller order $O_p(l/n)$, where $l$ is the
block length.  The expectation centering in $K_n(x)$ removes this minor
bias exactly but does not alter the first--order limit.  Consequently,
both corrections yield the same asymptotic distribution, and differences
appear only through higher--order terms that vanish as the sample size
increases.

To evaluate the finite--sample impact, we compared the two corrections
through additional simulations; see results in Section~2 in the
Supplement.  Across all sample sizes and dependence
levels considered, the empirical sizes and powers were nearly identical.
This finding supports the theoretical argument that the circular block
bootstrap already captures the leading effects of serial correlation,
leaving little residual bias for the expectation centering to remove.
The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
between them is largely immaterial in practice.  We therefore retain
$K_n(x)$ for theoretical completeness and consistency of presentation,
while acknowledging that either correction performs similarly in finite
samples.

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with seven levels of Kendall's
$\tau \in \{-.75, -.50, -.25, 0, .25, .50, .75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence between $X_i$ and
$X_{i+1}$ as it is invariant to monotone marginal
transformations.
To generate the samples to which our
method would be applied, we simulated a time series $W_i$ from a 1st
order autoregressive or AR(1) process:
\begin{equation*}
W_i = \phi W_{i-1} + \epsilon_i,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_i$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels:
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. The
series $W_i$ has mean zero and variance
$\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
$\phi$,  we
set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_i$ by
\begin{equation*}
X_i = F^{-1}[\Phi(W_i)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$
distribution and $\Phi$ is the distribution function of the standard normal
distribution.
Then we generated a marginal gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution. After the transformation
to the marginal gamma distribution, the lag-1 autocorrelations are approximately
\[
  \{-0.876, -0.674, -0.368, 0, 0.377, 0.701, 0.922\}.
\]

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions
are very similar and their first two moments are the same. For the purposes of
evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
marginal distribution is from the
Normal family, or
$X_i \sim N(\cdot ; \mu, \sigma^2), \quad i = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_i \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_i \sim \Gamma(\cdot ; \alpha, \beta), \quad i = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
As noted in Subsection~\ref{sub:npbb}, previous literature
suggests varying block size based on the dependence structure of the series.

For this reason, we also tried implementing our algorithm using the
plug-in approach for circular bootstrap block size introduced in
\citet{politis2004automatic}. Results and a discussion of this
additional simulation are provided in Section~2
in the Supplement. We also compared empirical performance for the
block bootstrap KS test when using the $K_n(x)$ correction
versus the $C_n(x)$. The $K_n(x)$ correction was used
in the main manuscript whereas results and a discussion for the
$C_n(x)$ correction is included in the supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method
10000 times to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating
process.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted $-0.75$ and 0.75 from this study because we already
found that our method doesn't work under the null hypothesis for such high
dependence levels under the sample sizes considered. It appears that the
rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial
dependence, but they do not seem to be affected by negative serial dependencies
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in
\jy{This inequality does not make sense.}
rejection rates close to 1 for $0.5 < \tau < 0.5$. 
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very
high (almost 1), indicating that under $H_A$, the test is very powerful
when a large enough sample size is used.

@@

***Section here describing practical conclusions/recommendations for
bias correction***

### 2025-10-04 manuscript/reply2.tex
revixed section 2.4 and replied AE

We thank the AE for this helpful comment. We have added a supplement
which includes a section on ``Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness}
Bias Correction''. We re-ran the simulation study from the main
manuscript, but we replaced the $K_n(x)$ bias correction with $C_n(x)$.
The results are discussed in the supplement, and are alluded to in the
main paper. Overall, we find that there is no noticeable improvement
in either size or power when using the $K_n(x)$ bias correction, even
for small sample sizes. With these results, we recommend ........

@@

Thank you for the suggestion, these investigations have now been
placed in the ``Performance of Nonparametric Block Bootstrap
Kolmogorov-Smirnov Test with Block Size Calibration'' of the new
supplement, and they are still referred to in the main manuscript.

>>>>

\textbf{Response to Comment on the Bias Correction Term.}

We thank the reviewer for raising this insightful question and for the
helpful suggestion to clarify the motivation for using $K_n(x)$ rather
than $C_n(x)$.  The previously confusing paragraph about the
``reliability'' of $F_n(x)$ and $\hat\theta_n$ has already been removed.
Section~2.4 now presents a streamlined discussion that first explains how
$K_n(x)$ centers the bootstrap KS process, then outlines the theoretical
justification for its use, and finally summarizes new simulation results.

A newly added paragraph clarifies that two bias corrections$C_n$ and
$K_n$ are asymptotically equivalent under independence and
short--memory dependence.  The preference for $K_n(x)$ arises from
theoretical considerations: under serial dependence, the bootstrap
analogue of $C_n(x)$ can exhibit a small $O_p(l/n)$ conditional bias
due to cross--lag covariances between $F_n(x)$ and $\hat\theta_n$,
where $l$ is the block length.  The expectation centering in $K_n(x)$
removes this bias without changing the first--order limit, yielding a
cleaner asymptotic argument.

To examine whether this refinement provides tangible benefits, we added
simulations comparing the two corrections.  Across all dependence levels
and sample sizes considered, the empirical sizes and powers were nearly
identical.  This outcome supports the theoretical result that both
methods converge to the same limit distribution and that the additional
expectation centering in $K_n(x)$ mainly improves conceptual symmetry
rather than finite--sample performance.  We have revised
Section~2.4 accordingly and added a brief reference in the Supplement to
document these findings.

@@

Thank you for the suggestion, these investigations have now been
placed in the ``Selection of Block Size'' of the newly added
supplement, and they are still referred to in the main manuscript.

### 2025-10-04 manuscript/supplement.tex
revixed section 2.4 and replied AE

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citep{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.

\bibliographystyle{asa}
\bibliography{citations}
\end{document}

>>>>

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citep{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.\bibliographystyle{asa}
\bibliography{citations}
\end{document}
